\documentclass[12pt]{article}

% Packages
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage[backend=biber, style=apa]{biblatex} % Use biblatex with biber
\usepackage{hyperref}

% Page layout
\geometry{a4paper, margin=1in}

% Bibliography file
\addbibresource{references.bib} % Specify the .bib file

% Title and Author
\title{Title of the Paper}
\author{Author Name}
\date{\today}

% ------------------------------------------------------------------------------
% Document
\begin{document}

\maketitle
% 1. Executive Summary
\section*{1. Executive Summary (max half page)}
% Your summary here.

% 2. Introduction
\section*{2. Introduction (about one page)}
\subsection*{(a) Cause and impact of economic fluctuations}
% Content here.

\subsection*{(b) Consequences for economy and why policy should act}
% Content here.

\subsection*{(c) Brief overview of suggested policy}
% Content here.



% ------------------------------------------------------------------------
% THEO ------------------------
% ------------------------------------------------------------------------

% 3. Bird’s Eye View of the Model
\section*{3. Bird’s Eye View of the Model (about two pages)}

\subsection*{(a) Outline of the Model Structure (graphical and verbal, no equations)}
% Content here (include figure environment if needed).

\subsection*{(b) Policy Structure of the Model (main equations)}
% Content here (use align or equation environments).

\subsection*{(c) Calibration of the Model}
% Content here.


% ------------------------------------------------------------------------
%  JAKUB -------------------------------
% ------------------------------------------------------------------------

% 4. Benchmark Model Analysis
\section*{4. Benchmark Model Analysis (about two pages)}
\subsection*{(a) How does the shock lead to economic fluctuations (baseline scenario)?}

As our scenario requires that the Central Bank adopts a money supply target, we adjust the benchmark model to a monetary policy rule with the following specification: $\frac{M_t}{M_{t-1}} = ()^\theta_{MC}(1+\pi_{t+1})$

\subsection*{(b) What is the idea behind the implemented policy (current policy scenario)?}
% Content here.
% ------------------------------------------------------------------------


% 5. Counterfactual Policies
\section*{5. Counterfactual Policies (about two pages)}
\subsection*{(a) More or less of the same policy (different coefficients)?}
% Content here.

\subsection*{(b) Alternative policy (different targets)?}
% Content here.

% -------------------------------------------------------
%                       NOTES
% -------------------------------------------------------
% - try adding in the labour supply target instead of MC
% - think about implementing alternative inflation target (0.03)
% - think about alternative monetary policy rules 
% -  fiscal instead of monetary as a counter-factual?




% -------------------------------------------------------


% 6. Policy Recommendation and Discussion
\section*{6. Policy Recommendation and Discussion (about one page)}
\subsection*{(a) Give a recommendation on policy based on your simulations.}
% Content here.

\subsection*{(b) Should policy have taken a different path?}
% Content here.

\subsection*{(c) Do your results confirm or conflict with your perception about optimal policy? Discuss how.}
% Content here.
% \printbibliography() % Print the bibliography

\end{document}